An Hypernetwork Approach to Accurately Measure Technological Innovation \bigskip\\ \textit{Project Proposal}

### 2015-10-20 Docs/Proposal/patents.tex
Update patents.tex

Two other indicators are of particular interest for us: originality and radicalness. The originality measure is
defined by Hall \textit{et al.} (2001) \cite{Hall2001} as
\[
O_{i}%
=1-\sum_{j=1}^{n_{i}}{c_{i,j}^{2}}\] where $c_{i,j}$
is the
percentage of citations made by patent $i$ to a patent in class $j$ out of
$n_{i}$ technological classes to which patent $i$ belongs. If the scope of
technologies which the patent uses and cites is large, then the originality
measure will be high. Radicalness is more difficult to define. It is
constructed in the same way as the originality index but here we only consider
the technology classes of patents cited by patent $i$ but to which patent $i$
does not belong. These two indicators are good proxies and great start to estimate if a patent is protecting a new product that can hardly be classified into the official technological field space.

@@

% TBW : useful ?

@@

% idem

@@

>>>>

Two other indicators are of particular interest for us: originality and radicalness. The originality measure is
defined by Hall \textit{et al.} (2001) \cite{Hall2001} as
\[
O_{i}%
=1-\sum_{j=1}^{n_{i}}{c_{i,j}^{2}} where $c_{i,j}$
is the
percentage of citations made by patent $i$ to a patent in class $j$ out of
$n_{i}$ technological classes to which patent $i$ belongs. If the scope of
technologies which the patent uses and cites is large, then the originality
measure will be high. Radicalness is more difficult to define. It is
constructed in the same way as the originality index but here we only consider
the technology classes of patents cited by patent $i$ but to which patent $i$
does not belong. These two indicators are good proxies and great start to estimate if a patent is protecting a new product that can hardly be classified into the official technological field space.

@@

We define a binary relation between each pair of patents $Cit(i, j)$ = 1 if j cites i or i cites j.

@@

For each patent i, let $B_i$ be the set of technological class of i. We then define a relationship between each pair i and j as 2 times the number of technological class in common divided by the total number of class of i and j. 
\[
Class(i,j) = 2\frac{\left\vert{B_i\cap B_j}\right\vert}{\frac{\left\vert{B_i}\right\vert}+\frac{\left\vert{B_j}\right\vert}}
\]

Thus, if two patents have no class in common, $Class(i,j)=0$ while if the two patents are exactly identical in terms of their sets of technologial class $Class(i,j)=1$.

@@

We first assign to a patent $p$ a set of significant keywords $K(p)\in $
